% !TEX program = xelatex

\documentclass[letterpaper]{resume}
\usepackage[hidelinks]{hyperref}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\geometry{top=0.25in,left=0.75in,bottom=0.25in,right=0.75in}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Junzhuo Wang}

% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\contactInfo{\href{mailto:junzhuow@usc.edu}{junzhuow@usc.edu}}{+1 213-453-5901}{1246 W 30th St, Los Angeles, CA}{\href{https://github.com/cs512}{cs512}}
% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

\section{\faInfoCircle\ Objective}
Seeking for an internship in Software Engineering.

\section{\faGraduationCap\ Education}
% \section{Education}
\datedsubsection{\textbf{University of Southern California}, Los Angeles, CA}{Jan. 2016 -- Present}
\textit{Master student} in Computer Science (CS), \textit{4.0/4}, expected Dec. 2017
\datedsubsection{\textbf{Tongji University}, Shanghai, China}{Sept. 2011 -- Jun. 2015}
\textit{B.S.} in Computer Science (CS), \textit{88.1/100}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Tongji-Yale Center of Advanced Networks and Networked Systems}}{Jul. 2015 -- Dec. 2015}
\role{Java, YANG;}{Software Development Internship}
\begin{itemize}
  \item Implemented Application-Layer Traffic Optimization(ALTO) module in OpenDayLight.
  \item Improved L2 Switch module in OpenDayLight(ODL) to cooperate with ALTO module.
  \item Deployed ALTO on Caltech's test environment.
  \item Submitted an IETF draft: \textit{"ALTO Extension: Endpoint Cost Service for Flows"}.
\end{itemize}

\datedsubsection{\textbf{MLW Limited}}{Feb. 2013 -- Jun. 2013}
\role{Javascript, HTML, CSS;}{Web Development Internship}
\begin{itemize}
  \item Built a web application by \textit{Angular.js}.
\end{itemize}

\section{\faCodeFork\ Projects}
\datedsubsection{\textbf{Space Defender}}{Aug. 2016 -- Present}
\role{Unity 3D, Blender, C\#;}{A spaceship Tower Defence game at \textit{GamePipe} in USC}

\datedsubsection{\textbf{Stock Market Inquirer}}{Jan. 2016 -- May 2016}
\role{Swift, PHP, HTML5, CSS, Javascript;}{An iOS application as course project for \textit{Web Technology} in USC}
\begin{itemize}
  \item Built application to retrieve stock historical and real-time information.
  \item Deployed back-end server on Amazon AWS to provide stock information.
\end{itemize}

\datedsubsection{\textbf{Furniture Preview System Based on Augmented Reality Technique}}{Jul. 2014}
\role{Python, Arduino, C++;}{A project of \textit{2014 Intel Cup Embedded System Design Contest}}
\begin{itemize}
  \item Built a glove with flex sensor and IMU to grab virtual furniture in augmented reality space.
  \item Implemented a positioning mechanism using gyro, accelerate meter and camera.
  \item Optimized performance for Intel Baytrail processor.
\end{itemize}

\datedsubsection{\textbf{Image retrieval system accelerated by CUDA}}{Nov. 2012 -- Feb. 2014}
\role{Python, CUDA C, SQL;}{A project of \textit{Shanghai Undergraduate Innovative Program at Tongji University}}
\begin{itemize}
  \item Built a web application to query back-end server to retrieve image.
  \item Implemented retrieve system by \textit{GPU-based SIFT} algorithm.
\end{itemize}

\datedsubsection{\textbf{Multiple Cycle CPU}}{Dec. 2013}
\role{Verilog;}{A course project of \textit{Computer Organization} in Tongji University}
\begin{itemize}
  \item Implemented a multi-cycle CPU soft core on Xilinx's FPGA by \textit{Verilog}.
\end{itemize}

\datedsubsection{\textbf{Linux File System}}{Aug. 2013}
\role{C, C++;}{A course project of \textit{Operating System} in Tongji University}
\begin{itemize}
  \item Implemented Linux file system and related system calls.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, Java, C++, C, Javascript, HTML5, CSS, C\#
  % \item Platform: Linux, macOS
  % \item Development: Web, Embedded System, 
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{3} Prize}, Award on 2014 Intel Cup Embedded System Design Contest}{Jul. 2014}
% \datedline{\textit{\nth{2} Prize}, Award on Program Design Contest in Tongji University}{May 2012}
% \datedline{\textit{\nth{1} Prize}, Award on National Olympiad in Informatics in Provinces}{Nov. 2011}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
